Setup Honeypot: Team Contagiarium

### 2011-10-31 Setup_honeypot.tex
Heb het eea toegevoegd

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

@@

We have configured this machine to log syslog messages coming from the honeypot.

@@

>>>>

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{appendix}
% These packages are all incorporated in the memoir class to one degree or another...

@@

In this section we decribe the setup of the utility machine.

\subsection{Syslog}
Syslog uses UDP to transmit its logfiles to a remote server and this is not very desirable, because everything is sent in plaintext and delivery is not garanteed.
A VPN session between the two hosts is possible, but might be considered as overkill and still does not garantee delivery.
Therefore we have configured syslog to use TCP, which makes it possible to use SSH to tunnel the TCP traffic.
We are using a reverse tunnel from the utility machine to the honeypot.
We use a script to allow the connection to be re-esthablished quickly when the SSH session is terminated for some reason. 
\cite{Remote_logging}

@@

\bibliographystyle{alpha}
\bibliography{ref_bib}
